\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{setspace}
\pagestyle{empty}
\hypersetup{colorlinks=true,urlcolor=blue}
\setstretch{0.98}
\setlength{\parskip}{0.45em}
\setlength{\parindent}{0pt}

\begin{document}

{\LARGE \textbf{Pranav Ramanathan}}\\
+44 7916 717 471\;|\;\href{mailto:pranav.ramanathan@gmail.com}{pranav.ramanathan@gmail.com}\\
\href{https://linkedin.com/in/pranav-ramanathan/}{LinkedIn}\;|\;
\href{https://github.com/pranav-ramanathan}{GitHub}\;|\;
\href{https://pranavramanathan.me}{Portfolio}

\vspace{0.4cm}
\today

\vspace{0.4cm}
Hiring Manager\\
Citadel Securities\\
London, UK

\vspace{0.3cm}
Dear Hiring Manager,

I am applying for the \textbf{Software Engineer Internship (London, 2026)} at Citadel Securities. I am completing a BSc in Mathematics at Queen Mary University of London (predicted First Class, graduating 2026) and will begin an MSc in Artificial Intelligence in 2026. Your internship's focus on building high-performing, resilient production systems in small teams is exactly the environment I want to grow in.

In my recent work, I have focused on performance, reliability, and rapid iteration. At TinyMagiq, I reduced query latency from 30 seconds to 0.5 seconds by redesigning retrieval pipelines for a multi-document AI system handling 30+ concurrent documents, and I reduced inference cost by over 95\% through model and infrastructure migration while maintaining quality. At Humanaize, I engineered and shipped a production AWS platform using short development cycles, CI/CD, and reliability-focused architecture across multiple deployments.

I also bring strong analytical grounding in probability, statistics, and optimization from my mathematics training and research experience. During my STRIDE internship, I benchmarked transformer and reinforcement learning methods against integer programming on combinatorial optimization tasks, built a Python reliability testing framework, and published a first-author preprint. This strengthened how I reason about trade-offs, evaluate system behavior, and communicate technical decisions clearly within collaborative teams.

I am excited by Citadel Securities' engineering culture of turning ambitious ideas into production technology quickly. I would value the opportunity to contribute to your internship program and learn from your engineers, researchers, and traders while building systems that support real-world market infrastructure.

Thank you for your time and consideration. I would welcome the opportunity to discuss my application.

Sincerely,\\[0.4cm]
Pranav Ramanathan

\end{document}
